Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-07-02 paper/paper.Rmd
fix env partitioning, remove deprecated `crs` arg

autoplot(resampling_buffer,
  size = 0.8, task = task, fold_id = 1, crs = 32717) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

autoplot(resampling_disc,
  size = 0.8, task = task, fold_id = 1, crs = 32717) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

autoplot(resampling_block_random,
  size = 0.8, fold_id = 1, task = task, crs = 32717,
  show_blocks = TRUE, show_labels = TRUE) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

autoplot(resampling_block_systematic,
  size = 0.8, fold_id = 1, task = task, crs = 32717,
  show_blocks = TRUE, show_labels = TRUE) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

autoplot(resampling_block_checkerboard,
  size = 0.8, fold_id = 1, task = task, crs = 32717,
  show_blocks = TRUE, show_labels = TRUE) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

autoplot(resampling_block_rows_cols,
  size = 0.8, fold_id = 1, task = task, crs = 32717,
  show_blocks = TRUE, show_labels = TRUE) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

autoplot(resampling_tiles,
  size = 0.8, fold_id = 1, task = task, crs = 32717) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

autoplot(resampling_coords,
  size = 0.8, fold_id = 1, task = task, crs = 32717) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

autoplot(resampling_cstf_time,
  fold_id = 5, task = task_spt, crs = 32717, plot3D = TRUE
)
```

@@

autoplot(resampling_cstf_loc,
  fold_id = 5, task = task_spt, crs = 32717, plot3D = TRUE)
```

@@

autoplot(resampling_cstf_time_loc,
  fold_id = 4, task = task_spt, crs = 32717, plot3D = TRUE,
  show_omitted = TRUE)
```

@@

Support for user-defined partitioning strategies is built into \pkg{mlr3} directly since version 0.12.0 FIXME.
Labelled as "Custom CV", users are able to supply an external factor vector with the same length as number of observations.
Alternatively to supplying an external factor vector, the name of a feature within the task can be used.

The following example was taken from `sperrorest::partition_factor()`.

FIXME: eval=TRUE when available upstream im mlr3
FIXME: add visualization when method is available

```{r custom-cv,  fig.cap="Custom resampling using an external factor vector.", out.width="40%", fig.pos="ht", eval=FALSE}
breaks = quantile(task$data()$dem, seq(0, 1, length = 6))
zclass = cut(task$data()$dem, breaks, include.lowest = TRUE)

@@

autoplot(resampling_custom,
  size = 0.8, fold_id = 1, task = task) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

autoplot(resampling_env,
  size = 0.8, fold_id = 1, task = task, crs = 32717,
  show_blocks = TRUE, show_labels = TRUE) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

autoplot(resampling_env_multi,
  size = 0.8, fold_id = 1, task = task, crs = 32717,
  show_blocks = TRUE, show_labels = TRUE) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

autoplot(resampling_sp, task, fold_id = c(1:2), crs = 32717, size = 0.8) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

autoplot(resampling_nsp, task, fold_id = c(1:2), crs = 32717, size = 0.8) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

>>>>

autoplot(resampling_buffer,
  size = 0.8, task = task, fold_id = 1) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

autoplot(resampling_disc,
  size = 0.8, task = task, fold_id = 1) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

autoplot(resampling_block_random,
  size = 0.8, fold_id = 1, task = task,
  show_blocks = TRUE, show_labels = TRUE) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

autoplot(resampling_block_systematic,
  size = 0.8, fold_id = 1, task = task,
  show_blocks = TRUE, show_labels = TRUE) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

autoplot(resampling_block_checkerboard,
  size = 0.8, fold_id = 1, task = task,
  show_blocks = TRUE, show_labels = TRUE) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

autoplot(resampling_block_rows_cols,
  size = 0.8, fold_id = 1, task = task,
  show_blocks = TRUE, show_labels = TRUE) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

autoplot(resampling_tiles,
  size = 0.8, fold_id = 1, task = task) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

autoplot(resampling_coords,
  size = 0.8, fold_id = 1, task = task) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

autoplot(resampling_cstf_time,
  fold_id = 5, task = task_spt, plot3D = TRUE
)
```

@@

autoplot(resampling_cstf_loc,
  fold_id = 5, task = task_spt, plot3D = TRUE)
```

@@

autoplot(resampling_cstf_time_loc,
  fold_id = 4, task = task_spt, plot3D = TRUE,
  show_omitted = TRUE)
```

@@

Support for user-defined partitioning strategies is built into \pkg{mlr3} directly since version 0.12.0 FIXME.
Labelled as "Custom CV", users are able to supply an external factor vector with the same length as number of observations.
Each level of the factor vector will result in one partition.
Alternatively to supplying an external factor vector, the name of a feature (type `character`) present within the task can be supplied via argument `col`.

The following example was taken from `sperrorest::partition_factor()` because the resulting partitions separate nicely from each other in a visual way.

```{r custom-cv, fig.cap="Custom resampling using an external factor vector defining the partitions. Each coloring represents one partition.", out.width="40%", fig.pos="ht"}
breaks = quantile(task$data()$dem, seq(0, 1, length = 6))
zclass = cut(task$data()$dem, breaks, include.lowest = TRUE)

@@

autoplot(resampling_custom, size = 0.8, task = task) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

autoplot(resampling_env,
  size = 0.8, fold_id = 1, task = task) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

autoplot(resampling_env_multi,
  size = 0.8, fold_id = 1, task = task) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

autoplot(resampling_sp, task, fold_id = c(1:2), size = 0.8) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

autoplot(resampling_nsp, task, fold_id = c(1:2), size = 0.8) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```
